Pangenome graph layout by Path-Guided Stochastic Gradient Descent

### 2023-09-18 manuscript/main.tex
move 2D fig into main part

@@

    \subsection{Pangenome graphs layouts reveal biology features}
	Graph visualization is essential for understanding pangenome graphs and the genome variation they represent. 
	We show how 2D PG-SGD allows us gaining insight into biological data by looking at the graph layout structure. 
	%To demonstrate this, we provide various 2D PG-SGD layouts in Figure~\ref{fig:2d_layouts}.

	In Figure~\ref{fig:2d_fig1}, the chromosomes of the HPRC graph show the large scale structural variations in the centromeres.
	Focusing on the major histocompatibility complex (MHC) of chromosome 6 (Figure~\ref{fig:2d_fig2}), the 2D layout reveals the positions and diversity of all MHC genes (Figure~\ref{fig:2d_fig3}).
	In Figure~\ref{fig:2d_fig4} the C4A and C4B genes are highlighted. 
	%The layout is the same as the one produced by \textit{Bandage}~\citep{Wick_2015} and displayed in~\citep{Guarracino2022}.
	Complementary, we provide various 1D visualizations of in Supplementary Figure~\ref{fig:1d_sorts}.

@@

	\begin{appendices}
	    \section{Supplementary data}
		\input{fig_2d_layouts}
	    %\subsection{Quantization} % DURING REVISION, IF NEEDED
	    %More details about your clever quantization.
	    \subsection{Performance evaluation}
	    \label{sec:performance}
	    The results of the performance evaluation are given in Table~\ref{tab:layout}.
	    \input{table_layout}
	    \FIXME{What about the SMT thingy?}
		\subsection{1D visualizations}	
		The 1D PG-SGD algorithm creates a 1D layout of the nodes of the graph.
		Theoretically, it is possible that 2 nodes have the same 1D coordinate or overlap.
		But, in our 1D visualizations, we arrange the nodes from left to right.
		Therefore, we project the 1D coordinates into a 1D node order: We sort the final layout by graph component, graph position, and node rank.
		\input{fig_1d_sorts}
	\end{appendices}

>>>>

% supplement stuff
\newcommand{\beginsupplement}{%
	\setcounter{table}{0}
	\renewcommand{\thetable}{S\arabic{table}}%
	\setcounter{figure}{0}
	\renewcommand{\thefigure}{S\arabic{figure}}%
}

@@

    \subsection{Pangenome graphs layouts reveal biology features}
	Graph visualization is essential for understanding pangenome graphs and the genome variation they represent. 
	We show how 2D PG-SGD allows us gaining insight into biological data by looking at the graph layout structure. 
	%To demonstrate this, we provide various 2D PG-SGD layouts in Figure~\ref{fig:2d_layouts}.
			\input{fig_2d_layouts}
	In Figure~\ref{fig:2d_fig1}, the chromosomes of the HPRC graph show the large scale structural variations in the centromeres.
	Focusing on the major histocompatibility complex (MHC) of chromosome 6 (Figure~\ref{fig:2d_fig2}), the 2D layout reveals the positions and diversity of all MHC genes (Figure~\ref{fig:2d_fig3}).
	In Figure~\ref{fig:2d_fig4} the C4A and C4B genes are highlighted. 
	%The layout is the same as the one produced by \textit{Bandage}~\citep{Wick_2015} and displayed in~\citep{Guarracino2022}.
	Complementary, we provide various 1D visualizations of in Supplementary Figure~\ref{fig:1d_sorts}.

@@

	\clearpage
	\setcounter{page}{1}

	\beginsupplement

	\section{Supplement}

	 \subsection{Supplementary data}
	 %\subsection{Quantization} % DURING REVISION, IF NEEDED
	 %More details about your clever quantization.
	 \subsubsection{Performance evaluation}
	 \label{sec:performance}
	 The results of the performance evaluation are given in Table~\ref{tab:layout}.
	 \input{table_layout}
	 %\FIXME{What about the SMT thingy?} % DURING REVISION, IF NEEDED
	\subsubsection{1D visualizations}	
	The 1D PG-SGD algorithm creates a 1D layout of the nodes of the graph.
	Theoretically, it is possible that 2 nodes have the same 1D coordinate or overlap.
	But, in our 1D visualizations, we arrange the nodes from left to right.
	Therefore, we project the 1D coordinates into a 1D node order: We sort the final layout by graph component, graph position, and node rank.
	\input{fig_1d_sorts}
